Semi-Permeable Vesicles: Mathematical Formulation, Numerics, and Physics

### 2020-07-02 vesicle_code/docs/permeableVes/main.tex
working on stenosis runs
removing asv files

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Poiseuille Flow}
We consider a semi-permeable vesicle in the Poiseuille flow $\uu =
U(1-(y/R)^2,0)$, where $R=10$ determines the flow width, and $U$ is the
maximum flow rate. The length of the vesicle is $L = 4\pi$ and its
initial reduced area is $\nu = 0.65$. In
Figure~\ref{fig:parabolicPhaseDiagram}, plot the steady state
configuration for a variety of flow rates $U$ and permeability rates
$\beta$. Similar to the shear example, we see that the flow rate has the
biggest effect on the final shape, and the effect of the permeability
rate is much weaker. Instead, the permeability rate determines the time
required for the vesicle to reach a steady state. In
Tables~\ref{tbl:parabolicRelaxTimes1}
and~\ref{tbl:parabolicRelaxTimes2}, we consider two flow rates and
report the time, $t_\mathrm{steady}$, required for the vesicle's area to
be within 1.3\% of its maximum area, and the time, $t_\mathrm{inflate}$,
required for the vesicle's area to exceed 1.3\% of its initial area. We
see that both times scale with $\beta^{-1}$.

@@

@@

%\input{figures/shearPhaseDiagramRA2.tikz}
%\input{figures/parabolicPhaseDiagram.tikz}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Poiseuille Flow}
We consider a semi-permeable vesicle in the Poiseuille flow $\uu =
U(1-(y/R)^2,0)$, where $R=10$ determines the flow width, and $U$ is the
maximum flow rate. The length of the vesicle is $L = 4\pi$ and its
initial reduced area is $\nu = 0.65$. We first investigate the the
effect of the flow rate $U$ and the permability rate $\beta$ on the
steady state shape of the vesicle when it is initially placed on the
center line $y=0$. Figure~\ref{fig:parabolicPhaseDiagram} shows the
steady state configuration for a variety of flow rates $U$ and
permeability rates $\beta$. Similar to the shear example, we see that
the flow rate has the biggest effect on the final shape while the
permeability rate has a much weaker effect. Instead, the permeability
rate determines the time required for the vesicle to reach a steady
state. In Tables~\ref{tbl:parabolicRelaxTimes1}
and~\ref{tbl:parabolicRelaxTimes2}, we consider two flow rates and
report the time, $t_\mathrm{steady}$, required for the vesicle's area to
be within 1.3\% of its maximum area, and the time, $t_\mathrm{inflate}$,
required for the vesicle's area to exceed 1.3\% of its initial area. We
see that both times scale with $\beta^{-1}$.

As a second experiment, we investigate the effect of $U$ and $\beta$
when the vesicle is initialized above line $y=0$. Kaoui et
al.~\cite{kao-bir-mis2009} analyzed the migration of the same
experiment, but with an impermeable vesicle. They showed that for
above a critical reduced area, the vesicle migrates to the center line
$y=0$ as a symmetric shape. However, for smaller reduced areas, the
limiting shape is a tank-treading slipper with a center of mass above
the center line $y=0$. We repeat this experiment but with a
semi-permeable vesicle.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Semi-Permeable Vesicle in Stenosis}
Inspired by an experiment that measured the effects of cells on the
dynamical pressure-drop variations along a micrometer-sized
channel~\cite{abk-fai-sto2006}, we consider a numerical experiment where
a semi-permeable vesicle passes through a constriction. We also measure
the pressure-drop variation by measuring the pressure at the inlet and
outlet of the constriction.

In each experiment, we initialize an elliptical vesicle with longest
diameter of 9$\mu$m. We use a length scale of $R_0 = 10^{-6}$m, a
bending stiffness of $k_b = 10^{-19}$J, and fluid viscosity of $\mu=5
\times 10^{-2}$kg/ms. Using the relaxation time scale $\tau = \mu
R_0^3/k_b = 5 \times 10^{-1}$s, the velocity scale is $U = 2 \times
10^{-6}$m/s, and the pressure scale is $P = k_b/R_0^3 = 10^{-1}$Pa.  The
geometry is similar to the experiment~\cite{abk-fai-sto2006} where the
membrane starts in a channel with diameter $25\mu$m and passes into a
channel with length $45\mu$m and diameter $5\mu$m. Our numerical methods
are unable to achieve the high-speed flow rate in the experiments, so we
consider a much smaller flow rate.

\begin{figure}[htp]
%  \ifTikz
  \input{figures/stenosisGeom.tikz}
%  \fi
%  \includegraphics[width=0.8\linewidth]{figures/parabolicPhaseDiagram.pdf}
  \caption{\label{fig:stenosisGeom} A caption.}
\end{figure}

@@

 \newpage
\input{figures/shearPhaseDiagramRA2.tikz}
%\input{figures/parabolicPhaseDiagram.tikz}
